---
title: Registration
code-fold: true
params:
    csv_dir: "private/csv"
    registration_fn: "registrations-2026.csv"
    presenters_fn: "presenters-2026.csv"
    sheets_fn: "Open Scholarship Bootcamp 2026: Registration (Responses)"
    reg_sheets_id: "1mM0rSuFS5_y2sQtU9AI9zm8kuOGeDzilJZdu1MUR8zk"
    psu_id: "rog1@psu.edu"
---

## About

This page documents and implements the data processing workflow for bootcamp registration.

## Setup

We load some packages into memory for convenience.

```{r}
#| label: load-packages
suppressPackageStartupMessages(library('tidyverse'))
suppressPackageStartupMessages(library('ggplot2'))
suppressPackageStartupMessages(library('dplyr'))
suppressPackageStartupMessages(library('tidyr'))
suppressPackageStartupMessages(library('stringr'))
suppressPackageStartupMessages(library('lubridate'))
suppressPackageStartupMessages(library('janitor'))
```

## Import

The Google Form generates a Google Sheet that we download to a protected directory (`private/csv`) that is *not* synched to GitHub.

::: {.callout-important}
This is because the sheet contains personally identifying information.

To implement this, we add `private` to our `.gitignore` file in the project's root directory. This omits all files in `private/` from version control and keeps them local to the machine we render the site from. 
:::

```{r}
#| label: import-data
#| message: false
#| 
x <- assertthat::is.string(params$csv_dir)
if (!dir.exists(params$csv_dir)) {
  message("Creating missing `include/csv/`.")
  dir.create(params$csv_dir)
}
x <- assertthat::is.writeable(params$csv_dir)

# options(gargle_oauth_email = Sys.getenv("GMAIL_SURVEY"))
# googledrive::drive_auth()

x <- assertthat::is.string(params$psu_id)
googlesheets4::gs4_auth(email = params$psu_id)

x <- assertthat::is.string(params$sheets_id)
registrations <- googlesheets4::read_sheet(params$reg_sheets_id,
                                           sheet = "Form Responses 1")
x <- assertthat::assert_that(is_tibble(registrations))

registration_full_fn <- file.path(params$csv_dir, params$registration_fn)
x <- assertthat::is.string(registration_full_fn)

readr::write_csv(registrations, file = registration_full_fn)
```

Download presenter data, too.

```{r}
#| label: download-save-program-committee
#| message: false

presenters <- googlesheets4::read_sheet(params$reg_sheets_id,
                                          sheet = "presenters")
x <- assertthat::assert_that(is_tibble(presenters))

x <- assertthat::is.string(params$presenters_fn)
presenters_full_fn <- file.path(params$csv_dir, params$presenters_fn)

readr::write_csv(presenters, file = presenters_full_fn)
```

## Clean

Google Forms conveniently returns the questions as variable names at the top of each column. These are handy for creating a data dictionary, but awkward for data processing. We rename these for our convenience. We also export a data dictionary.

```{r}
#| label: tbl-data-dictionary
#| tbl-cap: "A minimal data dictionary."

reqistrations_qs <- names(registrations)

registrations_clean <- registrations |>
  dplyr::rename(
    timestamp = "Timestamp",
    attend_days = "Which days of the bootcamp will you attend?",
    name = "What is your name?",
    psu_email = "Email Address",
    dept = "What is your department or unit?",
    position = "What is your current position?",
    comments = "Any comments?"
  )

registrations_short <- c(
  "timestamp",
  "psu_email",
  "attend_days",
  "name",
  "dept",
  "position",
  "comments"
)
registrations_pid <- c(FALSE, FALSE, FALSE, TRUE, FALSE, FALSE, FALSE)

registrations_dd <- data.frame(qs = reqistrations_qs, 
                               qs_short = registrations_short, 
                               pid = registrations_pid)

registrations_dd |>
  knitr::kable(format = 'html')

data_dict_fn <- file.path(params$csv_dir, "registrations-2026-data-dict.csv")
x <- assertthat::is.string(data_dict_fn)
readr::write_csv(registrations_dd,
                 file = data_dict_fn)
```

We drop some of responses that were used to test the workflow.

```{r}
registrations_clean <- registrations_clean |>
  dplyr::filter(psu_email != "nittany.amateur.radio.club@gmail.com")
```

## Visualize

### Registration numbers {-}

```{r}
#| label: create-subsetted-dfs
attendees_names <- registrations_clean$name
presenter_names <- presenters$Presenter
all_names <- unique(c(attendees_names, presenter_names))
```

As of `r Sys.Date()`, we have *n*=`r dim(registrations_clean)[1]` registered attendees. We also have *n*=`r length(presenter_names)` presenters. A handful of presenters also registered, so we have *n*=`r length(all_names)` unique attendees who plan to come.

That is `r round(100*(length(all_names))/75, 1)`\% of our target registration/attendance limit of *n*=75.

### Time series {-}

```{r}
#| label: fig-registration-time-series
#| fig-cap: "Time series of registrations."
registrations_clean |>
  dplyr::arrange(timestamp) |>
  dplyr::mutate(resp_index = seq_along(timestamp)) |>
  ggplot() +
  aes(x = timestamp, y = resp_index) +
  geom_point() +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x = NULL, y = 'n registrations') +
  scale_color_manual(breaks = c("No", "Yes"),
                        values=c("red", "green")) +
  theme(legend.position = "none")
```

<!-- ### Registrant attendance plans by day -->

<!-- ```{r} -->
<!-- #| label: tbl-registration-by-day -->
<!-- #| fig-cap: "Bootcamp registrations by day." -->
<!-- registrations_clean |> -->
<!--   dplyr::mutate(plan_mon = stringr::str_detect(attend_days, "Mon"), -->
<!--                 plan_tue = stringr::str_detect(attend_days, "Tue")) |> -->
<!--   dplyr::mutate(n_mon = sum(plan_mon, na.rm = TRUE), -->
<!--                 n_tue = sum(plan_tue, na.rm = TRUE)) |> -->
<!--   dplyr::select(n_mon, n_tue) |> -->
<!--   dplyr::distinct() |> -->
<!--   knitr::kable(format = "html") |> -->
<!--   kableExtra::kable_classic() -->
<!-- ``` -->

### Registrations by position

```{r}
#| label: fig-by-position
#| fig-cap: "Registrations by position."
registrations_clean |>
  dplyr::filter(!is.na(position)) |>
 dplyr::count(position, sort = TRUE) |>
  dplyr::mutate(position = fct_reorder(position, n)) |>
  ggplot() +
  geom_bar(aes(x = position, y = n), fill = "#96BEE6", stat = "identity") +
  scale_y_continuous(breaks = seq(0, 40, by = 5)) +
  theme(legend.position = "right") +
  theme(legend.title = element_blank()) +
  xlab("") +
  theme_classic() +
  coord_flip()
```

### Registrations by unit

Clean and recode.

```{r}
select_this <- registrations_clean$name == "Parisa Osfoori"
registrations_clean$dept[select_this] <- "Communication Sciences & Disorders"

select_this <- registrations_clean$name == "Koraly Pérez-Edgar"
registrations_clean$dept[select_this] <- "Psychology"

select_this <- registrations_clean$name== "Keyana Enayati"
registrations_clean$dept[select_this]  <- "PSU Harrisburg"
```

Normalize department names; assign college/institute values.

```{r by-dept}
registrations_clean <- registrations_clean |>
  dplyr::mutate(
    dept = dplyr::recode(
      dept,
      `Clinical Psychology` = "Psychology",
      `Psychology (Cognitive)` = "Psychology",
      `Psychology / SSRI` = "Psychology",
      `Psychology (Developmental)` = "Psychology",
      `Department of Psychology` = "Psychology",
      `Cognitive Psychology` = "Psychology",
      `Psychology, Developmental` = "Psychology",
      `Developmental Psychology (CAT Lab)` = "Psychology",
      `Developmental Psychology` = "Psychology",
      `Psych` = "Psychology",
      `College of Liberal Arts (psychology)` = "Psychology",
      
      `English language` = "English",
      `english` = "English",
      `English Language Teaching` = "English",
      `English Department` = "English",
      
      `Languages` = "Global Languages & Literatures",
      `Languages and Literature` = "Global Languages & Literatures",
      `Department of Foreign Languages` = "Global Languages & Literatures",
      
      `Linguistics` = "Applied Linguistics",
      
      `Department of Sociology and Criminology` = "Sociology & Criminology",
      
      `Communication Arts and Sciences` = "Communication Arts & Sciences",
      
      `Communication Sciences and Disorders` = "Communication Sciences & Disorders",
      `CSD` = "Communication Sciences & Disorders",
      
      `Human Development and Family Studies & Social Data Analytics` = "HDFS",
      `Human Development and Family Studies` = "HDFS",
      `Human Development and Family Studies (HDFS)` = "HDFS",
      `Department of Human Development and Family Studies` = "HDFS",
      `Human Development and Family Sciences` = "HDFS",
      `HDFS/DEMO` = "HDFS",
      
      `bbh` = "BBH",
      `Biobehavioral Health` = "BBH",
      `Biobehavioural Health` = "BBH",
      `Biobehavioural  Health` = "BBH",
      `Biobehavioral health` = "BBH",
      
      `RPTM` = "Recreation, Park, & Tourism Management",
      `Recreation, Park and Tourism Management` = "Recreation, Park, & Tourism Management",      
      `Sociology and Social Data Analytics` = "Sociology",
      `Spanish Italian and portuguese` = "Spanish, Italian, & Portuguese",
      `Spanish, Italian, and Portuguese Department` = "Spanish, Italian, & Portuguese",
      `Spanish Italian and Portuguese` = "Spanish, Italian, & Portuguese",
      `Spanish, Italian, and Portuguese` = "Spanish, Italian, & Portuguese",
      
      `French and Francophone Studies` = "French & Francophone Studies",
      
      `DEMOG` = "Demography",
      
      `Germanic & Slavic Languages & Literatures` = "German & Slavic Languages",
      `Germanic and Slavic Languages and Literatures` = "German & Slavic Languages",
      
      `Nutrition` = "Nutritional Sciences",
      
      `College of IST` = "IST",
      
      `Statistics Department` = "Statistics",
      `Department of Statistics` = "Statistics",
      `stat` = "Statistics",
      `statistic` = "Statistics",
      
      `Math` = "Mathematics",
      `Astronomy and Astrophysics` = "Astronomy & Astrophysics",

      `SHS` = "Student Health Svcs",
      
      `Department of Chemical Engineering` = "Chemical Engineering",
      
      `ESM` = "Engineering Science & Mechanics",
      `Engineering Science` = "Engineering Science & Mechanics",
      `Engineering Science and Mechanics` = "Engineering Science & Mechanics",
      
      `EECS` = "Electrical Engineering & Comp Sci",
      
      `Department of Food Science` = "Food Science",
      
      `Libraries` = "University Libraries",
      `University libraries` = "University Libraries",
      
      `Ecosystem Science and Management` = "Ecosystem Science & Management",
      
      `PRC` = "Population Research Center",
      
      `TLT, PSU Libraries` = "University Libraries",
      
      `Business and Economics` = "Business & Economics",
      
      `EE` = "Electrical Engineering",
      
      `College of Medicine / Clinical and Translational Science Institute` = "CTSI",
      `College of Medicine, CTSI` = "CTSI",
      
      `Mechanical engineering,Penn state Harrisburg` = "Mechanical Engineering (Harrisburg)",
      
      `Smeal College of Business, Accounting` = "Accounting",
      
      `School of Science, Engineering, and Technology` = "Sci, Engr, & Tech",
      
      `institute for Computational and Data Sciences` = "ICDS",
      
      `Plant Pathology and environmental microbiology` = "Plant Pathology & Environmental Microbiology",
      
      `Meteorology and Atmospheric Sciences` = "Meteorology & Atmospheric Sciences",
      
      `School of Labor and Employment Relations` = "School of Labor & Employment Relations",

      `PCD` = "Preservation Conservation & Digitization",
      
      `Vazquez Lab/Eberly College of Science/Bio` = "Biology",
      `Biology Department/ Vazquez lab` = "Biology",
      
      `WORKFORCE EDUCATION AND DEVELOPMENT` = "Workforce Education & Development",
      
      `Curriculum and Instructions` = "Curriculum & Instruction",
      
      `Kinesiology, HHD` = "Kinesiology",
      
      `BME` = "Biomedical Engineering",
      
      `Computer Science` = "Computer Science & Engineering",
      `Department of Computer Science and Engineering` = "Computer Science & Engineering",
      `College of Engineering/Computer Science` = "Computer Science & Engineering",
      
      `Ed Policy Studies` = "Education Policy Studies",
      
      `CHE` = "Chemical Engineering",
      
      `Agricultural and Biological Engineering` = "Agricultural & Biological Engineering",
      
      `Mechanical` = "Mechanical Engineering",
      
      `Health Administration` = "Health Policy & Administration",
      
      `CMPEN` = "Computer Engineering",

      `ESM/ REI` = "Engineering Science & Mechanics",
      
      `Civil Eng` = "Civil Engineering",
      
      `Meteorology and Atmospheric Science` = "Meteorology & Atmospheric Science",
      `Meteorology & Atmospheric Sciences` = "Meteorology & Atmospheric Science"
    )
  ) |>
  dplyr::mutate(
    college = recode_values(
      dept,
      "Agricultural & Biological Engineering" ~ "AgSci",
      "Ecosystem Science & Management" ~ "AgSci",
      "Entomology" ~ "AgSci",
      "Food Science" ~ "AgSci",
      "Plant Pathology & Environmental Microbiology" ~ "AgSci",
      "Plant Science" ~ "AgSci",
      
      "German & Slavic Languages" ~ "CLA",
      "Psychology" ~ "CLA",
      "Spanish, Italian, & Portuguese" ~ "CLA",

      "Anthropology" ~ "CLA",
      "Applied Linguistics" ~ "CLA",
      "Asian Studies" ~ "CLA",
      "C-SoDA" ~ "CLA",
      "Demography" ~ "CLA",
      "Communication Arts & Sciences" ~ "CLA",
      "Economics" ~ "CLA",
      "English" ~ "CLA",
      "French & Francophone Studies" ~ "CLA",
      "Global Languages & Literatures" ~ "CLA",
      "Office of Digital Pedagogies and Initiatives" ~ "CLA",
      "Political Science" ~ "CLA",
      "Sociology" ~ "CLA",
      "Sociology & Criminology" ~ "CLA",
      "School of Labor & Employment Relations" ~ "CLA",
      
      "Bellisario College of Communication" ~ "Comm",
      "Mass Communications" ~ "Comm",
      

      "Astronomy & Astrophysics" ~ "ECoS",
      "Biology" ~ "ECoS",
      "Chemistry" ~ "ECoS",
      "Integrative Science" ~ "ECoS",
      "Mathematics" ~ "ECoS",
      "Statistics" ~ "ECoS",

      "College of Education" ~ "Education",
      "LPS/LDT" ~ "Education",
      "Workforce Education & Development" ~ "Education",
      "Curriculum & Instruction" ~ "Education",
      "Education Policy Studies" ~ "Education",
      
      "Meteorology & Atmospheric Science" ~ "EMS",
      
      "Acoustics" ~ "Engineering",
      "Biomedical Engineering" ~ "Engineering",
      "Chemical Engineering" ~ "Engineering",
      "Chemical/Biomedical Engineering" ~ "Engineering",
      "Civil Engineering" ~ "Engineering",
      "College of Engineering" ~ "Engineering",
      "Computer Engineering" ~ "Engineering",
      "Computer Science & Engineering" ~ "Engineering",
      "Electrical Engineering & Comp Sci" ~ "Engineering",
      "Electrical Engineering" ~ "Engineering",
      "Engineering" ~ "Engineering",
      "Engineering Science & Mechanics" ~ "Engineering",
      "Material Science and Engineering" ~ "Engineering",
      "Mechanical Engineering" ~ "Engineering",

      "College of Human and Health Development" ~ "HHD",
      "Communication Sciences & Disorders" ~ "HHD",
      "BBH" ~ "HHD",
      "HDFS" ~ "HHD",
      "Kinesiology" ~ "HHD",
      "Nutritional Sciences" ~ "HHD",
      "Recreation, Park, & Tourism Management" ~ "HHD",

      "HHD" ~ "HHD",
      "Health Policy & Administration" ~ "HHD",
      
      "Biotechnology" ~ "Huck",
      "Plant Biology" ~ "Huck",
      
      "ICDS" ~ "ICDS",
      
      "IST" ~ "IST",
      "Data Analytics" ~ "IST",
      "Cybersecurity" ~ "IST",
      "Information Science and Technology" ~ "IST",
      
      "Preservation Conservation & Digitization" ~ "Libraries",
      "Research Informatics and Publishing" ~ "Libraries",
      "University Libraries" ~ "Libraries",
      
      "Neuroscience" ~ "Medicine",
      "Medicine" ~ "Medicine",
      "CTSI" ~ "Medicine",
      
      "College of Nursing" ~ "Nursing",
      
      "EESI" ~ "EESI",
      
      "Psychology (Harrisburg)" ~ "PSU Harrisburg",
      "PSU Harrisburg" ~ "PSU Harrisburg",
      "Mechanical Engineering (Harrisburg)" ~ "PSU Harrisburg",
      "PSU Harrisburg" ~ "PSU Harrisburg",
      "Sci, Engr, & Tech" ~ "PSU Harrisburg",
      
      "Business & Economics" ~ "PSU Brandywine",
      
      "Schreyer Institute for Teaching Excellence" ~ "Old Main",  
      
      "OVPR" ~ "OVPR",
      "ORP" ~ "OVPR",
      
      "Population Research Center" ~ "SSRI",

      "Accounting" ~ "Smeal",
      "Marketing" ~ "Smeal",
      
      "University of Kansas, Psychology" ~ "UKansas"

    ),
    .default = "Unknown",
    .missing = "Unknown"
  )
```

Plot.

```{r}
#| label: fig-regis-dept-coll
#| fig-cap: "Registrations by college/unit."
registrations_clean |>
  dplyr::filter(!is.na(college)) |>
  dplyr::count(college, sort = TRUE) |>
  dplyr::mutate(college = fct_reorder(college, n)) |>
  ggplot() +
  geom_bar(aes(x = college, y = n), fill = "#BF8226", stat = "identity") +
  scale_y_continuous(breaks = seq(2, 24, by = 2)) +
  theme(legend.position = "right") +
  theme(legend.title = element_blank()) +
  xlab("") +
  theme_classic() +
  coord_flip()
```

The bootcamp registrations represent *n*=`r length(unique(registrations_clean$dept))` departments and *n*=`r length(unique(registrations_clean$college))` campuses, colleges, institutes, or administrative entities.
